Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-08-02 paper/ms.tex
updated subsection on the dark matter halo number density

In addition to the uncertainties in the astrophysical processes describing
star formation in galactic populations, is the calculation of the fraction of \ly photons
that escape the galaxy to the observer is another debated step. Given the resonant nature of
the \ly line, the radiative transfer of \ly is sensitive to the
density, temperature, topology and kinematics of the neutral Hydrogen
in the interstellar medium (ISM). \citep{Neufeld1991,ForeroRomero2011,
  Dijkstra2012,Laursen2013,Orsi2012}.

@@

The main purpose of this section is to show how different
observational constraints narrow down the parameters space of allowed
models. In each one of the four sub-sections we add a new
constraint. First we consider the average halo number density, then we
consider the surface density distributions for all the mock fields in
a given mock survey. From this result we move to narrower constraints
by requiring a high number of mock surveys with consistent surface
density distributions to finally consider the impact of the angular
correlation function.

@@

This result provides the basis to understand why only a specific range of models
${\mathcal M}$ can be expected to be consistent with
observations. From Figure \ref{fig:halos} we can read that models
with a minimum mass $\log_{10} M_{\rm min}>11.5$\hMsun \ will always have a
surface number density lower than the observational
constrain. This makes impossible that models with that minimum mass
can be compatible with observations.

The opposite is true in models with $\log_{10} M_{\rm min}<10.5$
that will show surface number density larger than observations, this
implies that in such models the occupation fraction has to be tuned
$f_{\rm occ}<1.0$ as to lower the halo number density to match the
gray band values.

In the next subsection we quantify this intuition by means of the
Kolmogorov-Smirnov tests between mock surveys and observations.

>>>>

In addition to the uncertainties in the astrophysical processes
describing star formation in galactic populations, is the calculation
of the fraction of \ly photons that escape the galaxy to the observer
is another debated step. Given the resonant nature of the \ly line,
the radiative transfer of \ly is sensitive to the density,
temperature, topology and kinematics of the neutral Hydrogen in the
interstellar medium
(ISM). \citep{Neufeld1991,ForeroRomero2011,Dijkstra2012,Laursen2013,Orsi2012}.

@@

The main purpose of this section is to show how different
observational constraints narrow down the parameters space of allowed
models. Each sub-sections presents the effect of adding new pieces of
observational or statistical evidence.

@@

This result provides the basis to understand why only a specific range of models
${\mathcal M}$ can be expected to be consistent with
observations. From Figure \ref{fig:halos} we can read that models with
a minimum mass $\log_{10} M_{\rm min}>11.5$\hMsun will always have a
surface number density lower than the observational
constrain. This makes impossible that models in that range can be
compatible with observations, there are simply to few halos compared
to observed LAEs.

The opposite is true in models with $\log_{10} M_{\rm min}<10.5$ that
have a surface number density larger than observations. In those cases
the occupation fraction $f_{\rm occ}<1.0$ can be tuned in order to
lower the halo number density to match observations.

Figure \ref{fig:halos} also illustrates the impact of cosmic
variance. At fixed mass there is an scatter of $0.3-0.6$ dex in the
mass range $10^{10}\hMsun < M_{\rm  min}<10^{11}\hMsun$.  A consequence of
this variation is that models with the same mass range and occupation
fraction can have mock fields with number densities varying up to a
factor of $\sim 2-5$. Also, the scatter in mocks across the simulation
is comparable to the $0.3$ dex scatter in observations.

In the same Figure \ref{fig:halos} we see that at fixed number
density, around the range allowed by observations, there is an scatter
in the masses of $0.4-0.5$ dex. This intrinsic scatter in the masses
with a given number density adds is also included in the mock
construction process, enlarging the range of possible models
consistent with observations.
